### 2019-07-08 pubs/paper/sections/proof-reconstruction/resolve.tex
Renamed folder itp-2018 to paper

In~\cite{Prieto-Cubides2017a}, we describe our first attempt to reconstruct this
rule that performs reordering of formulas jointly with the application of a
customized version of the resolution theorem to reconstruct the rule.
Unfortunately, that approach suffers of an exponential computational cost for
each searching by reordering the formulas. This time, we propose an alternative
formulation to reconstruct this rule as a particular case of the \fsimplify rule.
This observation was taken from the \TSTP derivations in order to improve
the timing of the type-checking. Futher improvements are future work.

>>>>

In~\cite{Prieto-Cubides2017a}, we describe our first attempt to reconstruct this
rule that performs reordering of formulas jointly with the application of a
customized version of the resolution theorem to reconstruct the rule.
Unfortunately, that approach suffers of an exponential computational cost for
each searching to reorder the formulas. Therefore, we propose
in~\label{eq:resolve} an alternative formulation to reconstruct this rule by
using the \fsimplify rule. This observation was taken from the \TSTP derivations
and we check that improves significantly the timing of the type-checking.
